BSOS

### 2014-06-08 Paper.tex
Fixed unsupported characters and added names.

\part{Fundamental Theory of Operating Systems}
\paragraph{Theory}
An Operating System has several different components. All software has to go through the OS in order for the user to be able to utilize any of the hardware. The kernel offers a basic level of control over doing this. The kernel manages memory access for programs in the RAM, determines which programs connect with which hardware, handles the CPU’s operating states, organizes data in the long run, and orders processes in multi-tasking systems. Essentially, the kernel assigns memory space.

\paragraph{Interrupts}
Interrupts are also very important. Interrupts create an efficient way for the OS to interact with its environment. Older systems used to monitor different sources of input for events. Interrupts help automatically save local register contexts and run particular code in response to particular events. Interrupts cause the current program to pause for a moment, save it, and then run code associated with that interrupt. In other words, an interrupt interrupts the program – hence the name, “interrupt”. The kernel handles interrupts.

@@

\paragraph{Boot}
When a computer initially turns on, it runs in supervisor mode. The first programs to run have unlimited access to hardware. When the OS allows another program to take control, the computer transitions into protected mode, where programs’ access to the CPU’s set of instructions is limited. To leave protected mode, an interrupt has to be triggered so that way the kernel will be able to take charge once again.

@@

\part{Booting Up}
BSOS's bootstrapping process can be classified by architecture.

@@

\part{Memory Management}

@@

\part{Interfacing With Hardware}

@@

\\Once all the drivers are in place and running, it's a simple matter to call their functionality from within the OS kernel, making the data sent and recieved readily usable by all programs on the device. (See section 3.)

>>>>

\part{Operating System Basics-Reyna}
\paragraph{Theory}
An Operating System has several different components. All software has to go through the OS in order for the user to be able to utilize any of the hardware. The kernel offers a basic level of control over doing this. The kernel manages memory access for programs in the RAM, determines which programs connect with which hardware, handles the CPU's operating states, organizes data in the long run, and orders processes in multi-tasking systems. Essentially, the kernel assigns memory space.

\paragraph{Interrupts}
Interrupts are also very important. Interrupts create an efficient way for the OS to interact with its environment. Older systems used to monitor different sources of input for events. Interrupts help automatically save local register contexts and run particular code in response to particular events. Interrupts cause the current program to pause for a moment, save it, and then run code associated with that interrupt. In other words, an interrupt interrupts the program-hence the name. Interupts are handles by the kernel.

@@

\paragraph{Boot}
When a computer initially turns on, it runs in supervisor mode. The first programs to run have unlimited access to hardware. When the OS allows another program to take control, the computer transitions into protected mode, where programs' access to the CPU's set of instructions is limited. To leave protected mode, an interrupt has to be triggered so that way the kernel will be able to take charge once again.

@@

\part{Booting Up-William}
BSOS's bootstrapping process can be classified by architecture.

@@

\part{Memory Management- Pawe\l{}}

@@

\part{Interfacing With Hardware-Alex}

@@

\\Once all the drivers are in place and running, it's a simple matter to call their functionality from within the OS kernel, making the data sent and recieved readily usable by all programs on the device. (See Parts 1 and 3)
